---
title: "p8105_hw5_hz2770"
author: "Hao Zheng"
date: "11/16/2021"
output: github_document
---

```{r}
library(tidyverse)
```

```{r}
# read the csv
homicide_data = read.csv("./data/homicide_data.csv", na = c(" ", "Unknown"))
```


## Problem 1
The dataset contains 52179 homicide cases and 12 variables including the date, victim's demographic information, city, state, precise longitude and latitude, and disposition status.

Then we create a new variable called `city_state`, and show the number of all homicides and unsolved homicides in each `city_state`.
```{r}
homicide_data = 
  homicide_data %>% 
  mutate(city_state = str_c(city, ", ", state)) %>% 
  relocate(city_state) %>% 
  filter(city_state != "Tulsa, AL")


summary_data = 
  homicide_data %>% 
  group_by(city_state) %>% 
  summarise(
    total_homicides = n(),
    unsolved_homicides = sum(disposition %in% c("Closed without arrest", "Open/No arrest"))
  )

knitr::kable(summary_data)
```

Then we perform a prop.test for the city Baltimore, MD, and get the estimate proportion and confidence interval.
```{r}
baltimore =
  summary_data %>% 
  filter(city_state == "Baltimore, MD")

# prop.test for baltimore, MD
balt_prop =
  prop.test(
    x = baltimore %>% pull(unsolved_homicides),
    n = baltimore %>% pull(total_homicides)
  ) %>% 
  broom::tidy()

balt_prop

# pull the estimate proportion and 95% confidence interval
pull(balt_prop, estimate)
pull(balt_prop, conf.low)
pull(balt_prop, conf.high)
```

Now, we can perform `prop.test` for every city, and get the estimate proportion and confidence interval.
```{r}
city_prop = 
  summary_data %>% 
  mutate(
    prop_test = map2(.x = unsolved_homicides, .y = total_homicides, ~prop.test(x = .x, n = .y)),
    tidy_test = map(.x = prop_test, ~broom::tidy(.x))
  ) %>% 
  select(-prop_test) %>% 
  unnest(tidy_test) %>% 
  select(city_state, estimate, conf.low, conf.high)
```

Create a plot to show above results.

```{r}
city_prop %>% 
  mutate(
    city_state = fct_reorder(city_state, estimate)
  ) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  labs(
    x = "city",
    y = "estimate",
    title = "Estimates and CIs for unsolved proportions across different cities"
  ) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```


## Problem 2

```{r}
# get the path
path = str_c(
  "./data/zip_data/", list.files("./data/zip_data/")
  )

study_data = tibble(
  file_name = list.files("./data/zip_data/"),
  subjects = purrr::map(path, read_csv)
) %>% 
  mutate(file_name = str_remove(file_name, ".csv")) %>% 
  separate(file_name, c("control_arm", "subject_ID"), sep = "_") %>%
  mutate(
    subject_ID = as.numeric(subject_ID),
    control_arm = as.factor(control_arm),
    control_arm = recode(control_arm, con = "control_group", exp = "experiment_group")
  ) %>% 
  unnest(subjects) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    names_prefix = "week_",
    values_to = "observations"
  ) %>% 
  mutate(week = as.numeric(week))

# show the tidied dataframe
study_data
```


Make a spaghetti plot.
```{r}
study_data %>% 
  ggplot(aes(x = week, y = observations, group = subject_ID)) +
  facet_grid(.~control_arm) +
  geom_line() +
  labs(
    x = "week",
    y = "observations",
    title = "weekly observations in different arms"
  )
```

From the spaghetti plot, we can see that the experiment arm has an overall increasing trend as time goes by, while the control arm has a rather stable value with a little fluctuation.


## Problem 3
```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

Write a function to fill in the missing values for two cases, and apply this function to the columns of `iris_with_missing`.

```{r}
fill_in_missing = function(x){
  # case 1 : replace missing values in numeric variables with the mean of non-missing values
  if(is.numeric(x)){
    x = ifelse(is.na(x), mean(x, na.rm = TRUE), x)
  }
  
  # case 2 :replace missing values in character variables with "virginica"
  else if(is.character(x)){
    x = ifelse(is.na(x), "Virginica", x)
  }
  
  return(x)
}

iris_with_replace = map(iris_with_missing, fill_in_missing)

iris_with_replace %>%
  as_tibble() %>%
  knitr::kable()
```

